Medical Concept Extraction

### 2012-12-14 paper/paper.tex
Adding more scaffolding to the paper TeX document.

\vspace{1in}

@@

\vspace{1in}

\section{Domain Specific Challenges}

\subsection{Sparse Data}

\vspace{1in}

\section{Algorithm}
Our system considers each document to be a stream of words grouped by sentences, and it attempts to provide the correct concept classification for each of those words. In order to identify the appropriate concept, our system considers natural language features for each document at successively broader contexts. Specifically, we first consider features using only the word itself as context, second we consider features which span the whole sentence , and last we consider n-gram features.

@@

\subsection{Dimension Compression}

@@

\subsubsection{Data Organization \& Directory Structure}

@@

\subsection{System Performance}

@@

Training time

\subsection{Evaluation}

@@

\subsection{Discussion}

@@

I don't know, BS something...

>>>>

@@

\section{Challenges}

\subsection{High Dimensionality}

\subsection{Biased Data}

\subsection{Amount of Data}

Low amounts of train data with high amounts of tests data.

\subsection{Data Usage Agreements}

\section{Design}
Our system considers each document to be a stream of words grouped by sentences, and it attempts to provide the correct concept classification for each of those words. In order to identify the appropriate concept, our system considers natural language features for each document at successively broader contexts. Specifically, we first consider features using only the word itself as context, second we consider features which span the whole sentence , and last we consider n-gram features.

\subsection{Data Flow \& Classification Task}

@@

@@

\subsubsection{Data Organization and Directory Structure}

@@

\subsection{Runtime Performance}

@@

\subsection{Classification Performance}

@@

\section{Discussion}

@@

\subsection{Dimension Collapse}

\subsection{Feature Selection}

\subsection{Parameter Selection}

\subsection{More Data}
